---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
options(width = 100)
Sys.setlocale("LC_COLLATE", "en_US.UTF-8") # ensure common sorting envir
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
ver <- desc::desc_get_version(".")
ver <- paste0("https://img.shields.io/badge/Version-", ver,
              "-success.svg?style=flat&logo=github")
```

# gitr

<!-- badges: start -->
![GitHub version](`r ver`)
[![CRAN status](http://www.r-pkg.org/badges/version/gitr)](https://cran.r-project.org/package=gitr)
[![R-CMD-check](https://github.com/stufield/gitr/workflows/R-CMD-check/badge.svg)](https://github.com/stufield/gitr/actions)
[![](https://cranlogs.r-pkg.org/badges/grand-total/gitr)](https://cran.r-project.org/package=gitr)
[![Codecov test coverage](https://codecov.io/gh/stufield/gitr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/stufield/gitr?branch=main)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
<!-- badges: end -->


A light-weight, dependency-free, application programming interface
(API) to access system-level [Git](https://git-scm.com/downloads) commands from within `R`.
Contains wrappers and defaults for common data science workflows as well as
[Zsh](https://github.com/ohmyzsh/ohmyzsh) plugin aliases (see below).
A generalized API syntax is also available.
A system installation of [Git](https://git-scm.com/downloads) is required.


If you run into any issues/problems with `gitr` full documentation
of the most recent
[release](https://github.com/stufield/gitr/releases)
can be found at the
[pkgdown website](https://stufield.github.io/gitr/).
If the issue persists I encourage you to consult the
[issues](https://github.com/stufield/gitr/issues/)
page and, if appropriate, submit an issue and/or feature request.


## Disclaimer

Use at own risk :smiley_cat:, however, PRs are encouraged for ideas that I've missed.
The functionality contained in `gitr` are _heavily_ influenced by __my__
personal data science workflows and may not suit all users.
However, if you have an idea that would make the package better,
more widely usable, and/or efficient, please submit an
[issue](https://github.com/stufield/gitr/issues/)
or
[pull request](https://github.com/stufield/gitr/pulls/).


## Installing

The easiest way to install `gitr` is to install directly from
[CRAN](https://CRAN.R-project.org/package=gitr)


```{r install-cran, eval = FALSE}
install.packages("gitr")
```

Alternatively install the development version from GitHub:

```{r install-gh, eval = FALSE}
remotes::install_github("stufield/gitr")
```

To install a *specific* tagged release, use:

```{r install-version, eval = FALSE}
remotes::install_github("stufield/gitr@v0.0.2")
```


-----------

## Loading

```{r load}
library(gitr)
```


## Examples

Here are some basic examples of the functionality grouped by common
actions:

#### Basics
```{r ver}
git_version()
```

```{r current}
gitr_current_br()
```

```{r default}
gitr_default_br()
```

```{r local}
gitr_local_br()
```


#### The Core Engine

```{r git-core}
(git("branch", "foo"))

git("branch", "-av")$stdout |>
  cat(sep = "\n")

git("branch", "-D", "foo")$stdout
```


#### Committing

```{r commit-msgs}
gitr_commit_msgs(n = 3)
```

```{r glog}
glog(5)
```

```{r commit-diff, eval = FALSE}
git_diffcommits()
```

```{r reset-hard, eval = FALSE}
git_reset_hard()
```

```{r reset-soft, eval = FALSE}
git_reset_soft()
```

```{r uncommit, eval = FALSE}
git_uncommit()
```

```{r unstage, eval = FALSE}
git_unstage("DESCRIPTION")
```


#### Secure Hash Algorithm (SHA-1)

```{r sha}
is_sha("d670c93733f3e1d7c95df7f61ebf6ca0476f14e3")

is_sha(c("foo", "d670c93"))   # vectorized

gitr_trim_sha("d670c93733f3e1d7c95df7f61ebf6ca0476f14e3")

gitr_trim_sha(c("foo", "d670c93"))   # vectorized

gitr_current_sha()
```


#### Tags

```{r tag-recent}
gitr_recent_tag()
```

```{r tag-info}
gitr_tag_info()
```


#### Situation Report

```{r sitrep}
gitr_sitrep()
```



--------


## ZSH-aliases available in `gitr`

| alias                 | git command                               |
| :-------------------- | :---------------------------------------- |
| `ga()`                | `git add`                                 |
| `gst()`               | `git status`                              |
| `gss()`               | `git status -s`                           |
| `gau()`               | `git add -u`                              |
| `gaa()`               | `git add --all`                           |
| `gb()`                | `git branch`                              |
| `gba()`               | `git branch -a`                           |
| `gbd()`               | `git branch -d/-D`                        |
| `gdf()`               | `git diff <file>`                         |
| `gbnm()`              | `git branch --no-merged`                  |
| `gbmm()`              | `git branch --merged`                     |
| `gbr()`               | `git branch --remote`                     |
| `gac()`, `gcn`        | `git commit --no-verify --no-edit --amend`|
| `gcc()`               | `git commit`                              |
| `gco()`               | `git checkout`                            |
| `gcb()`               | `git checkout -b`                         |
| `gcm()`               | `git checkout git_default_br()`           |
| `gcf()`               | `git config --list`                       |
| `gnuke()`             | `git reset --hard && git clean -dfx`      |
| `gcmsg()`             | `git commit -m`                           |
| `gp()`                | `git push`                                |
| `gpu()`               | `git push -u`                             |
| `gpd()`               | `git push --dry-run`                      |
| `gpf()`               | `git push --force-with-lease`             |
| `gpr()`               | `git pull --rebase --autostash -v`        |
| `glog()`              | `git log --oneline --decorate --graph`    |
| `gwip()`              | `git add -u && commit --no-verify -m "wip"` |
| `gclean()`            | `git clean -f -d`                         |
| `grm()`               | `git rm`                                  |
| `grmc()`              | `git rm --cached`                         |
| `gsta()`              | `git stash`                               |
| `gstl()`              | `git stash list`                          |
| `gpop()`,`gstp()`     | `git stash pop`                           |
| `gstaa()`             | `git stash apply`                         |
| `gstd()`              | `git stash drop`                          |
| `gstc()`              | `git stash clear`                         |
| `gsts()`              | `git stash show --text`                   |
| `gtn()`               | `git tag -n`                              |
| `grba()`              | `git rebase --abort`                      |
| `grbc()`              | `git rebase --continue`                   |
| `grbs()`              | `git rebase --skip`                       |
| `grbm()`              | `git rebase git_default_br()`             |
| `grv()`               | `git remote -v`                           |



-------------


## Full list of ZSH-aliases

For general reference, here is a list of the available aliases via the
`git-plugin` from [Oh-My-Zsh](https://github.com/ohmyzsh/ohmyzsh).

See also [Oh-My-Zsh](https://ohmyz.sh) for general installation.

#### Aliases

| alias            | git command                                       |
| :--------------- | :----------------------------------------------- |
| `gapa`           | `git add --patch`                                 |
| `gav`            | `git add --verbose`                               |
| `gloga`          | `git log --oneline --decorate --graph --all`      |
| `gup`            | `git pull --rebase`                               |
| `gupv`           | `git pull --rebase -v`                            |
| `gupa`           | `git pull --rebase --autostash`                   |
| `gupav`          | `git pull --rebase --autostash -v`                |
| `gap`            | `git apply`                                       |
| `gapt`           | `git apply --3way`                                |
| `gbda`           | `git branch --no-color --merged \| command grep -vE ^([+*] \| \s*($(git_main_branch) \| $(git_develop_branch))\s*$) \| command xargs git branch -d 2>/dev/null` |
| `gbl`            | `git blame -b -w`                                 |
| `gbs`            | `git bisect`                                      |
| `gbsb`           | `git bisect bad`                                  |
| `gbsg`           | `git bisect good`                                 |
| `gbsr`           | `git bisect reset`                                |
| `gbss`           | `git bisect start`                                |
| `gca`            | `git commit -v -a`                                |
| `gca!`           | `git commit -v -a --amend`                        |
| `gcan!`          | `git commit -v -a --no-edit --amend`              |
| `gcans!`         | `git commit -v -a -s --no-edit --amend`           |
| `gcam`           | `git commit -a -m`                                |
| `gcsm`           | `git commit -s -m`                                |
| `gcas`           | `git commit -a -s`                                |
| `gcasm`          | `git commit -a -s -m`                             |
| `gcl`            | `git clone --recurse-submodules`                  |
| `gcor`           | `git checkout --recurse-submodules`               |
| `gcd`            | `git checkout $(git_develop_branch)`              |
| `gcount`         | `git shortlog -sn`                                |
| `gcp`            | `git cherry-pick`                                 |
| `gcpa`           | `git cherry-pick --abort`                         |
| `gcpc`           | `git cherry-pick --continue`                      |
| `gcs`            | `git commit -S`                                   |
| `gcss`           | `git commit -S -s`                                |
| `gcssm`          | `git commit -S -s -m`                             |
| `gdca`           | `git diff --cached`                               |
| `gdcw`           | `git diff --cached --word-diff`                   |
| `gdct`           | `git describe --tags $(git rev-list --tags --max-count=1)` |
| `gds`            | `git diff --staged`                               |
| `gdt`            | `git diff-tree --no-commit-id --name-only -r`     |
| `gdup`           | `git diff @{upstream}`                            |
| `gdw`            | `git diff --word-diff`                            |
| `gf`             | `git fetch`                                       |
| `gfo`            | `git fetch origin`                                |
| `gfg`            | `git ls-files \| grep`                            |
| `gg`             | `git gui citool`                                  |
| `gga`            | `git gui citool --amend`                          |
| `ggpur`          | `ggu`                                             |
| `ggpull`         | `git pull origin $(git_current_branch)`           |
| `ggpush`         | `git push origin $(git_current_branch)`           |
| `ggsup`          | `git branch --set-upstream-to=origin/$(git_current_branch)`|
| `gpsup`          | `git push --set-upstream origin $(git_current_branch)`     |
| `ghh`            | `git help`                                        |
| `gignore`        | `git update-index --assume-unchanged`             |
| `gignored`       | `git ls-files -v \| grep "^[[:lower:]]"`          |
| `git-svn-dcommit-push` | `git svn dcommit && git push github $(git_main_branch):svntrunk` |
| `gl`             | `git pull`                                        |
| `glg`            | `git log --stat`                                  |
| `glgp`           | `git log --stat -p`                               |
| `glgg`           | `git log --graph`                                 |
| `glgga`          | `git log --graph --decorate --all`                |
| `glgm`           | `git log --graph --max-count=10`                  |
| `glo`            | `git log --oneline --decorate`                    |
| `glol`           | `git log --graph --pretty`                        |
| `glols="git log --graph --pretty` | `%Cred%h%Creset -%C(auto)%d%Creset %s %Cgreen(%ar) %C(bold blue)<%an>%Creset' --stat"`
| `glod="git log --graph --pretty`  | `%Cred%h%Creset -%C(auto)%d%Creset %s %Cgreen(%ad) %C(bold blue)<%an>%Creset'"`
| `glods="git log --graph --pretty` | `%Cred%h%Creset -%C(auto)%d%Creset %s %Cgreen(%ad) %C(bold blue)<%an>%Creset' --date=short"`
| `glola="git log --graph --pretty` | `%Cred%h%Creset -%C(auto)%d%Creset %s %Cgreen(%ar) %C(bold blue)<%an>%Creset' --all"`
| `gm`             | `git merge`                                       |
| `gmom`           | `git merge origin/$(git_main_branch)`             |
| `gmtl`           | `git mergetool --no-prompt`                       |
| `gmtlvim`        | `git mergetool --no-prompt --tool=vimdiff`        |
| `gmum`           | `git merge upstream/$(git_main_branch)`          |
| `gma`            | `git merge --abort`                               |
| `gpf!`           | `git push --force`                                |
| `gpoat`          | `git push origin --all && git push origin --tags` |
| `gpv`            | `git push -v`                                     |
| `gr`             | `git remote`                                      |
| `gra`            | `git remote add`                                  |
| `grb`            | `git rebase`                                      |
| `grbd`           | `git rebase $(git_develop_branch)`                |
| `grbi`           | `git rebase -i`                                   |
| `grbo`           | `git rebase --onto`                               |
| `grev`           | `git revert`                                      |
| `grh`            | `git reset`                                       |
| `grhh`           | `git reset --hard`                                |
| `groh`           | `git reset origin/$(git_current_branch) --hard`   |
| `grmv`           | `git remote rename`                               |
| `grrm`           | `git remote remove`                               |
| `grs`            | `git restore`                                     |
| `grset`          | `git remote set-url`                              |
| `grss`           | `git restore --source`                            |
| `grst`           | `git restore --staged`                            |
| `grt`            | `cd $(git rev-parse --show-toplevel \|\| echo .)` |
| `gru`            | `git reset --`                                    |
| `grup`           | `git remote update`                               |
| `gsb`            | `git status -sb`                                  |
| `gsd`            | `git svn dcommit`                                 |
| `gsh`            | `git show`                                        |
| `gsi`            | `git submodule init`                              |
| `gsps`           | `git show --pretty=short --show-signature`        |
| `gsr`            | `git svn rebase`                                  |
| `gstu`           | `gsta --include-untracked`                        |
| `gstall`         | `git stash --all`                                 |
| `gsu`            | `git submodule update`                            |
| `gsw`            | `git switch`                                      |
| `gswc`           | `git switch -c`                                   |
| `gswm`           | `git switch $(git_main_branch)`                   |
| `gswd`           | `git switch $(git_develop_branch)`                |
| `gts`            | `git tag -s`                                      |
| `gtv`            | `git tag \| sort -V`                              |
| `gtl`            | `gtl(){ git tag --sort=-v:refname -n -l ${1}* }; noglob gtl` |
| `gunignore`      | `git update-index --no-assume-unchanged`          |
| `gunwip`         | `git log -n 1 \| grep -q -c "\-\-wip\-\-" && git reset HEAD~1` |
| `glum`           | `git pull upstream $(git_main_branch)`            |
| `gwch`           | `git whatchanged -p --abbrev-commit --pretty=medium` |
| `gam`            | `git am`                                          |
| `gamc`           | `git am --continue`                               |
| `gams`           | `git am --skip`                                   |
| `gama`           | `git am --abort`                                  |
| `gamscp`         | `git am --show-current-patch`                     |


#### LICENSE

Please note that this package is released with
a [LICENSE](https://github.com/stufield/gitr/blob/main/LICENSE.md).
By using in this package you agree to abide by its terms.

