---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
options(width = 101)
Sys.setlocale("LC_COLLATE", "en_US.UTF-8") # ensure common sorting envir
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

ver <- desc::desc_get_version(".")
ver <- paste0("https://img.shields.io/badge/Version-", ver,
              "-success.svg?style=flat&logo=github")
```

# The `gitr` Package

<!-- badges: start -->
![GitHub version](`r ver`)
[![CRAN status](http://www.r-pkg.org/badges/version/gitr)](https://cran.r-project.org/package=gitr)
[![R-CMD-check](https://github.com/stufield/gitr/workflows/R-CMD-check/badge.svg)](https://github.com/stufield/gitr/actions)
[![Codecov test coverage](https://codecov.io/gh/stufield/gitr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/stufield/gitr?branch=main)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
<!-- badges: end -->

## Overview

A light-weight, dependency-free, API to access system-level 'git'
commands from within `R`.
It contains wrappers and defaults for common data science workflows as well as
[Z-shell](https://github.com/ohmyzsh/ohmyzsh) and it's plugins (see below).
Generalized API syntax is also available.
A system installation of 'git' is required.

## Disclaimer

Use at own risk :smiley_cat:, however, PRs are encouraged for ideas that I've missed.
The functionality contained in `gitr` are _heavily_ influenced by __my__
personal data scienct workflows and may not suit all users.
However, if you have an idea that would make the package better,
more widely usable, and/or efficient, please submit an
[issue](https://github.com/stufield/gitr/issues/)
or
[Pull Request](https://github.com/stufield/gitr/pulls/).


## Installation

The easiest way to install `gitr` is to install directly from CRAN:

```{r install-cran, eval = FALSE}
install.packages("gitr")
```

Alternatively install the development version from GitHub:

```{r install-gh, eval = FALSE}
remotes::install_github("stufield/gitr")
```

To install a *specific* tagged release, use:

```{r install-version, eval = FALSE}
remotes::install_github("stufield/gitr@v0.0.1")
```


-----------

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(gitr)
```

```{r default}
git_default_br()
```

```{r current}
git_current_br()
```

```{r ver}
git_version()
```

```{r glog}
glog()
```

```{r sitrep}
git_sitrep()
```

--------


## ZSH-aliases available in `gitr`

| alias               | git command                              |
| :------------------ | :--------------------------------------- |
| `ga()`              | git add                                  |
| `gst()`             | git status                               |
| `gss()`             | git status -s                            |
| `gau()`             | git add -u                               |
| `gaa()`             | git add --all                            |
| `gb()`              | git branch                               |
| `gba()`             | git branch -a                            |
| `gbd()`             | git branch -d/-D                         |
| `gdf()`             | git diff <file>                          |
| `gbnm()`            | git branch --no-merged                   |
| `gbmm()`            | git branch --merged                      |
| `gbr()`             | git branch --remote                      |
| `gac()`, `gcn`      | git commit --no-verify --no-edit --amend |
| `gcc()`             | git commit                               |
| `gco()`             | git checkout                             |
| `gcb()`             | git checkout -b                          |
| `gcm()`             | git checkout `git_default_br()`          |
| `gcf()`             | git config --list                        |
| `gnuke()`,gpristine | git reset --hard && git clean -dfx       |
| `gcmsg()`           | git commit -m                            |
| `gp()`              | git push                                 |
| `gpu()`             | git push -u                              |
| `gpd()`             | git push --dry-run                       |
| `gpf()`             | git push --force-with-lease              |
| `gpr()`             | git pull --rebase --autostash -v         |
| `glog()`            | git log --oneline --decorate --graph     |
| `gwip()`            | git add -u && commit --no-verify -m "wip"|
| `gclean()`          | git clean -f -d                          |
| `grm()`             | git rm                                   |
| `grmc()`            | git rm --cached                          |
| `gsta()`            | git stash                                |
| `gstl()`            | git stash list                           |
| `gpop()`,`gstp()`   | git stash pop                            |
| `gstaa()`           | git stash apply                          |
| `gstd()`            | git stash drop                           |
| `gstc()`            | git stash clear                          |
| `gsts()`            | git stash show `--text`                  |
| `gtn()`             | git tag -n                               |
| `grba()`            | git rebase --abort                       |
| `grbc()`            | git rebase --continue                    |
| `grbs()`            | git rebase --skip                        |
| `grbm()`            | git rebase `git_default_br()`            |
| `grv()`             | git remote -v                            |



-------------


## Full list of ZSH-aliases

For general reference, here is a list of the available aliases via the
`git-plugin` from [Oh-My-Zsh](https://github.com/ohmyzsh/ohmyzsh).

See also [Oh-My-Zsh](https://ohmyz.sh) for general installation.

| alias           | git command                              |
| :-------------- | :--------------------------------------- |
| gapa            | git add --patch                          |
| gav             | git add --verbose                        |
| gloga           | git log --oneline --decorate --graph --all |
| gup             | git pull --rebase                        |
| gupv            | git pull --rebase -v                     |
| gupa            | git pull --rebase --autostash            |
| gupav           | git pull --rebase --autostash -v         |
| gap             | git apply                                |
| gapt            | git apply --3way'                        |
| gbda            | git branch --no-color --merged | command grep -vE ^([+*]|\s*($(git_main_branch)|$(git_develop_branch))\s*$) | command xargs git branch -d 2>/dev/null
| gbl             | git blame -b -w                          |
| gbs             | git bisect                               |
| gbsb            | git bisect bad                           |
| gbsg            | git bisect good                          |
| gbsr            | git bisect reset                         |
| gbss            | git bisect start                         |
| gca             | git commit -v -a                         |
| gca!            | git commit -v -a --amend                 |
| gcan!           | git commit -v -a --no-edit --amend       |
| gcans!          | git commit -v -a -s --no-edit --amend    |
| gcam            | git commit -a -m                         |
| gcsm            | git commit -s -m                         |
| gcas            | git commit -a -s                         |
| gcasm           | git commit -a -s -m                      |
| gcl             | git clone --recurse-submodules           |
| gcor            | git checkout --recurse-submodules        |
| gcd             | git checkout \$(git_develop_branch)      |
| gcount          | git shortlog -sn                         |
| gcp             | git cherry-pick                          |
| gcpa            | git cherry-pick --abort                  |
| gcpc            | git cherry-pick --continue               |
| gcs             | git commit -S                            |
| gcss            | git commit -S -s                         |
| gcssm           | git commit -S -s -m                      |
| gdca            | git diff --cached                        |
| gdcw            | git diff --cached --word-diff            |
| gdct            | git describe --tags \$(git rev-list --tags --max-count=1)
| gds             | git diff --staged                        |
| gdt             | git diff-tree --no-commit-id --name-only -r |
| gdup            | git diff @{upstream}                     |
| gdw             | git diff --word-diff                     |
| gf              | git fetch                                |
| gfo             | git fetch origin                         |
| gfg             | git ls-files \| grep                     |
| gg              | git gui citool                           |
| gga             | git gui citool --amend                   |
| ggpur           | ggu                                      |
| ggpull          | git pull origin \$(git_current_branch)   |
| ggpush          | git push origin \$(git_current_branch)   |
| ggsup           | git branch --set-upstream-to=origin/$(git_current_branch) |
| gpsup           | git push --set-upstream origin \$(git_current_branch)     |
| ghh             | git help                                 |
| gignore         | git update-index --assume-unchanged      |
| gignored        | git ls-files -v | grep "^[[:lower:]]"    |
| git-svn-dcommit-push | git svn dcommit && git push github \$(git_main_branch):svntrunk
| gk              | \gitk --all --branches &!                |
| gke             | \gitk --all \$(git log -g --pretty=%h) &! |
| gl              | git pull                                 |
| glg             | git log --stat                           |
| glgp            | git log --stat -p                        |
| glgg            | git log --graph                          |
| glgga           | git log --graph --decorate --all         |
| glgm            | git log --graph --max-count=10           |
| glo             | git log --oneline --decorate             |
| glol            | git log --graph --pretty | %Cred%h%Creset -%C(auto)%d%Creset %s %Cgreen(%ar) %C(bold blue)<%an>%Creset'"
| glols="git log --graph --pretty | %Cred%h%Creset -%C(auto)%d%Creset %s %Cgreen(%ar) %C(bold blue)<%an>%Creset' --stat"
| glod="git log --graph --pretty | %Cred%h%Creset -%C(auto)%d%Creset %s %Cgreen(%ad) %C(bold blue)<%an>%Creset'"
| glods="git log --graph --pretty | %Cred%h%Creset -%C(auto)%d%Creset %s %Cgreen(%ad) %C(bold blue)<%an>%Creset' --date=short"
| glola="git log --graph --pretty | %Cred%h%Creset -%C(auto)%d%Creset %s %Cgreen(%ar) %C(bold blue)<%an>%Creset' --all"
| gm              | git merge                                |
| gmom            | git merge origin/$(git_main_branch)      |
| gmtl            | git mergetool --no-prompt                |
| gmtlvim         | git mergetool --no-prompt --tool=vimdiff |
| gmum            | git merge upstream/\$(git_main_branch)   |
| gma             | git merge --abort                        |
| gpf!            | git push --force                         |
| gpoat           | git push origin --all && git push origin --tags |
| gpv             | git push -v                              |
| gr              | git remote                               |
| gra             | git remote add                           |
| grb             | git rebase                               |
| grbd            | git rebase \$(git_develop_branch)        |
| grbi            | git rebase -i                            |
| grbo            | git rebase --onto                        |
| grev            | git revert                               |
| grh             | git reset                                |
| grhh            | git reset --hard                         |
| groh            | git reset origin/\$(git_current_branch) --hard |
| grmv            | git remote rename                        |
| grrm            | git remote remove                        |
| grs             | git restore                              |
| grset           | git remote set-url                       |
| grss            | git restore --source                     |
| grst            | git restore --staged                     |
| grt             | cd \$(git rev-parse --show-toplevel \|\| echo .) |
| gru             | git reset --                             |
| grup            | git remote update                        |
| gsb             | git status -sb                           |
| gsd             | git svn dcommit                          |
| gsh             | git show                                 |
| gsi             | git submodule init                       |
| gsps            | git show --pretty=short --show-signature |
| gsr             | git svn rebase                           |
| gstu            | gsta --include-untracked                 |
| gstall          | git stash --all                          |
| gsu             | git submodule update                     |
| gsw             | git switch                               |
| gswc            | git switch -c                            |
| gswm            | git switch $(git_main_branch)            |
| gswd            | git switch $(git_develop_branch)         |
| gts             | git tag -s                               |
| gtv             | git tag | sort -V                        |
| gtl             | gtl(){ git tag --sort=-v:refname -n -l ${1}* }; noglob gtl |
| gunignore       | git update-index --no-assume-unchanged   |
| gunwip          | git log -n 1 | grep -q -c "\-\-wip\-\-" && git reset HEAD~1 |
| glum            | git pull upstream \$(git_main_branch)    |
| gwch            | git whatchanged -p --abbrev-commit --pretty=medium |
| gam             | git am                                   |
| gamc            | git am --continue                        |
| gams            | git am --skip                            |
| gama            | git am --abort                           |
| gamscp          | git am --show-current-patch              |



#### LICENSE

Please note that this package package is released with
a [LICENSE](https://github.com/stufield/gitr/blob/main/LICENSE.md).
By using in this package you agree to abide by its terms.


----------

Created by [Rmarkdown](https://github.com/rstudio/rmarkdown)
(v`r utils::packageVersion("rmarkdown")`) and `r R.version$version.string`.
